---
title: "Initial Korean covid 19"
author: "Amia Little"
date: "07/21/24"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```

# Introduction



### Data is from the Patient_Info dataset from          South Korea 1 Jan to 1 May 2020  
### This data was retrieved from a downloadable zip file from kaggle  

Some of the data was uncoded for sex - sex must be just male or female  
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well      
  
# Your Question - Is dying independent of sex?


# Methods
 
result is a categorical variable,sex is  categorical,
result depends on sex, we use helper file   
cat~cat     


## Graphical results - use ggplot commands to do this  

```{r}
barchartGC(~result + Sex,data=kRdata)
barchartGC(~ + result,data=kRdata,
type="percent")

```      
This barchart shows that more males died than females.

  





  
## Numerical results

```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```
The numerical summary shows that 64 percent of males died and 36 percent of females died. 
Twice the amount of males have died than females.

## Inferential results 




## Conclusions

